---
title: "TAXXI Taxonomic Assignment Metrics Comparison"
author: "Zack Gold"
date: "12/08/2020"
output: html_document
---

```{r}
library(tidyverse)
library(here)
```

# Load and Clean Data 
```{r}
all_Data <- read.table(file =here("Data","TAXXI","summary_taxxi_runs_10142020.txt"))

# Clean Up data Frame
all_Data %>% as.data.frame() %>% 
  dplyr::select( Comparison =V1, BLCA_score = V2, Taxonomic_rank = V5, Metric = V3, Value = V6) %>% 
  mutate(., Taxonomic_rank = recode(Taxonomic_rank, 
                                   `s`="Species",
                                   `g`="Genus",
                                   `f`="Family",
                                   `c`="Class",
                                   `o`="Order",
                                   `p`="Phylum",
                                   `d`="Domain",) ) %>% 
  mutate(., Metric = recode(Metric, 
                                   `Acc`="Accuracy",
                                   `MCR`="Misclassification Rate",
                                   `OCR`="Over-classification Rate",
                                   `TPR`="True Positive Rate",
                                   `UCR`="Under-classification Rate ") )-> all_Data_df

all_Data_df$BLCA_score <- as.numeric(all_Data_df$BLCA_score)
all_Data_df$Value <- as.numeric(all_Data_df$Value)
```

```{r}
#Colors for plotting
library(wesanderson)
wes_palette("GrandBudapest1") -> moon1
wes_palette("GrandBudapest2") -> moon2
wes_palette("Moonrise3") -> moon3

```

# TAXXI Summary Statistics

### Global Reference Database Assigned by Global Reference Database
```{r}
all_Data_df$Taxonomic_rank<- as.factor(all_Data_df$Taxonomic_rank)
all_Data_df$Taxonomic_rank <- ordered(all_Data_df$Taxonomic_rank, levels = c("Phylum","Class","Order",  "Family",
 "Genus",
 "Species"))

all_Data_df %>% 
  mutate(., Value = replace_na(Value, 0)) %>% 
  pivot_wider(names_from = Metric, values_from=Value) %>%
  mutate(., Sensitivity = 100*`True Positive Rate` / (`True Positive Rate` + `Under-classification Rate `),
         Specificity = 100-(`Misclassification Rate`+`Over-classification Rate`)) %>% 
  pivot_longer(cols = `True Positive Rate`:`Specificity`, names_to = "Metric",values_to ="Value") ->all_Data_df
```

```{r}
all_Data_df %>% 
  filter(., Comparison=="global_trim_vs_global_trim") %>% 
  ggplot(., aes(y=Value/100, x=BLCA_score, color=Taxonomic_rank, group=Taxonomic_rank)) +geom_line(size = 1, alpha=0.7) +facet_wrap(~Metric) + ggtitle(label = "Global Reference Database Assigned by Global Reference Database") +  scale_color_manual(name = "Taxonomic Rank", values=c(moon3[-1],moon2[2],moon2[4])) + ylab("Percent") + xlab("Bootstrap Confidence Score") + scale_y_continuous(labels = scales::percent) + theme_bw() +
  theme(axis.text.x= element_text(size=16),                                                                          axis.text.y= element_text(size=16),
        axis.title=element_text(size=18,face="bold"),
        strip.text.x = element_text(size=18),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18))-> taxxi_gvg

taxxi_gvg
```

```{r}
ggsave(filename = here("Data","TAXXI","Figures","taxxi_gvg.eps"),
       plot = taxxi_gvg,
       device = cairo_ps,
       dpi = 300,
       width = 14,
  height = 8,
  units = c("in"))

```



### Local Reference Database Assigned by Global Reference Database

```{r}

all_Data_df %>% 
  filter(., Comparison=="global_trim_vs_local_trim") %>% 
  ggplot(., aes(y=Value/100, x=BLCA_score, color=Taxonomic_rank, group=Taxonomic_rank)) +geom_line(size = 1, alpha=0.7) +facet_wrap(~Metric) + ggtitle(label = "Regional Reference Database Assigned by Global Reference Database") +  scale_color_manual(name = "Taxonomic Rank", values=c(moon3[-1],moon2[2],moon2[4])) + ylab("Percent") + xlab("Bootstrap Confidence Cutoff Score") + scale_y_continuous(labels = scales::percent) + theme_bw() +
  theme(axis.text.x= element_text(size=16),                                                                          axis.text.y= element_text(size=16),
        axis.title=element_text(size=18,face="bold"),
        strip.text.x = element_text(size=18),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18))-> taxxi_gvl
taxxi_gvl
```

```{r}
ggsave(filename = here("Data","TAXXI","Figures","taxxi_gvl.eps"),
       plot = taxxi_gvl,
       device = cairo_ps,
       dpi = 300,
       width = 14,
  height = 8,
  units = c("in"))

```

### Local Reference Database Assigned by Local Reference Database

```{r}
all_Data_df %>% 
  filter(., Comparison=="local_trim_vs_local_trim") %>% 
  ggplot(., aes(y=Value/100, x=BLCA_score, color=Taxonomic_rank, group=Taxonomic_rank)) +geom_line(size = 1, alpha=0.7) +facet_wrap(~Metric) + ggtitle(label = "Regional Reference Database Assigned by Regional Reference Database") +  scale_color_manual(name = "Taxonomic Rank", values=c(moon3[-1],moon2[2],moon2[4])) + ylab("Percent") + xlab("Bootstrap Confidence Cutoff Score") + scale_y_continuous(labels = scales::percent) + theme_bw()+
  theme(axis.text.x= element_text(size=16),                                                                          axis.text.y= element_text(size=16),
        axis.title=element_text(size=18,face="bold"),
        strip.text.x = element_text(size=18),
        legend.text=element_text(size=16),
        legend.title=element_text(size=18)) -> taxxi_lvl
taxxi_lvl
```

```{r}
ggsave(filename = here("Data","TAXXI","Figures","taxxi_lvl.eps"),
       plot = taxxi_lvl,
       device = cairo_ps,
       dpi = 300,
       width = 14,
  height = 8,
  units = c("in"))
```

## Accuracy
### Local Reference Database Assigned by Global Reference Database
```{r}
all_Data_df %>% 
  mutate(., Value = replace_na(Value, 0)) %>% 
  filter(., Comparison=="global_trim_vs_local_trim") %>% 
  filter(., Metric=="Accuracy") %>% 
  filter(., Taxonomic_rank=="Species") %>% 
  summarise(., max(Value), mean(Value), min(Value))
```
### Local Reference Database Assigned by Local Reference Database

```{r}
all_Data_df %>% 
  mutate(., Value = replace_na(Value, 0)) %>% 
  filter(., Comparison=="local_trim_vs_local_trim") %>% 
  filter(., Metric=="Accuracy") %>% 
  filter(., Taxonomic_rank=="Species") %>% 
  summarise(., max(Value), mean(Value), min(Value))
```

## Misclassification Rate

### Local Reference Database Assigned by Global Reference Database


```{r}
all_Data_df %>% 
  mutate(., Value = replace_na(Value, 0)) %>% 
  filter(., Comparison=="global_trim_vs_local_trim") %>% 
  filter(., Metric=="Misclassification Rate") %>% 
  filter(., Taxonomic_rank=="Species") %>% 
  summarise(., max(Value), mean(Value), min(Value))
```

### Local Reference Database Assigned by Local Reference Database

```{r}
all_Data_df %>% 
  mutate(., Value = replace_na(Value, 0)) %>% 
  filter(., Comparison=="local_trim_vs_local_trim") %>% 
  filter(., Metric=="Misclassification Rate") %>% 
  filter(., Taxonomic_rank=="Species") %>% 
  summarise(., max(Value), mean(Value), min(Value))
```

### Local Reference Database Assigned by Global Reference Database

```{r}
all_Data_df %>% 
  mutate(., Value = replace_na(Value, 0)) %>% 
  filter(., Comparison=="global_trim_vs_local_trim") %>% 
  filter(., Metric=="Misclassification Rate") %>% 
  filter(., Taxonomic_rank=="Species") %>% 
  filter(., BLCA_score < 61) %>% 
  summarise(., max(Value), mean(Value), min(Value))
```

### Local Reference Database Assigned by Local Reference Database

```{r}
all_Data_df %>% 
  mutate(., Value = replace_na(Value, 0)) %>% 
  filter(., Comparison=="local_trim_vs_local_trim") %>% 
  filter(., Metric=="Misclassification Rate") %>% 
  filter(., Taxonomic_rank=="Species") %>% 
    filter(., BLCA_score < 61) %>% 
  summarise(., max(Value), mean(Value), min(Value))
```

## Under-classification Rate

### Local Reference Database Assigned by Global Reference Database

```{r}
all_Data_df %>% 
  mutate(., Value = replace_na(Value, 0)) %>% 
  filter(., Comparison=="global_trim_vs_local_trim") %>% 
  filter(., Metric=="Under-classification Rate ") %>% 
  filter(., Taxonomic_rank=="Species") %>% 
  summarise(., max(Value), mean(Value), min(Value))
```

### Local Reference Database Assigned by Local Reference Database

```{r}
all_Data_df %>% 
  mutate(., Value = replace_na(Value, 0)) %>% 
  filter(., Comparison=="local_trim_vs_local_trim") %>% 
  filter(., Metric=="Under-classification Rate ") %>% 
  filter(., Taxonomic_rank=="Species") %>% 
  summarise(., max(Value), mean(Value), min(Value))
```

### Global reference Database Assigned by Global Reference database Taxonomic cutoff score 60 results
```{r}
all_Data_df %>% 
  mutate(., Value = replace_na(Value, 0)) %>% 
  filter(., Comparison=="global_trim_vs_global_trim") %>% 
  filter(., BLCA_score==60) %>% 
  filter(., Taxonomic_rank=="Species")
```

```{r}

write.csv(all_Data_df,file = here("Data","TAXXI","TAXXI_summary.csv"))
```


### Contignency Table

```{r}
all_Data_df %>% 
  mutate(., Value = replace_na(Value, 0)) %>% 
  filter(., Comparison=="global_trim_vs_global_trim") %>% 
  filter(., BLCA_score==60) %>% 
  filter(., Taxonomic_rank=="Species") 
  

all_Data_df %>% 
  mutate(., Value = replace_na(Value, 0)) %>% 
  filter(., Comparison=="global_trim_vs_local_trim") %>% 
  filter(., BLCA_score==60) %>% 
  filter(., Taxonomic_rank=="Species") 

all_Data_df %>% 
  mutate(., Value = replace_na(Value, 0)) %>% 
  filter(., Comparison=="local_trim_vs_local_trim") %>% 
  filter(., BLCA_score==60) %>% 
  filter(., Taxonomic_rank=="Species") 
  
```